\documentclass[a4paper,12pt,oneside]{book}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{times}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{tabu}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{caption}
\usepackage{listings}  % for highlighting source code.
\usepackage{color}
  \lstset{ % General setup for the package
	  language=Python,
  	basicstyle=\small\sffamily,
	  numbers=left,
  	numberstyle=\tiny,
  	frame=tb,
	  tabsize=2,
	  columns=fixed,
	  showstringspaces=false,
	  showtabs=false,
	  keepspaces,
	  commentstyle=\color{red},
	  keywordstyle=\color{blue}
  }

%Defining some new commands for some repeated text.
%Modify your name and other details in this section.
\newcommand{\theauthor}{Tushar Gautam}
\newcommand{\therollno}{114113089}
\newcommand{\thedegree}{B.Tech}
\newcommand{\thedegreelong}{Bachelor of Technology}
\newcommand{\thetitle}{Intelligent estimation of heating and cooling
load requirements of buildings}
\newcommand{\theguide}{Dr.K.Panneerselvam}
\newcommand{\thecoguide}{Dr.E.S.Gopi}
\newcommand{\thehod}{Dr.M.Duraiselvam}
\newcommand{\thedepartment}{Production Engineering}
\newcommand{\theyear}{2017}
\newcommand{\theacadyear}{2016-2017}
\newcommand{\themonth}{April}
\newcommand{\E}{\mathrm{E}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Corr}{\mathrm{Corr}}



%Adjusting the caption settings
\captionsetup[figure]{labelfont=bf, textfont=bf}
\captionsetup[table]{labelfont=bf, textfont=bf, position=top}

%Set paragraph indentation to zero
\setlength\parindent{0pt}
%Set paragraph spacing
\setlength{\parskip}{12pt}

%Set the paper size and the margins
\geometry{a4paper, tmargin=1in, rmargin=1in, bmargin=1in, lmargin=1.5in}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

%Format the chapter headings to be 14pt, centered and Uppercase
\titleformat{\chapter}[display]
  {\large\bfseries\centering}
  {\MakeUppercase\chaptertitlename\ \thechapter}{7pt}{\large\MakeUppercase}

%Format the section headings to be uppercase and 12pt
\titleformat{\section}[hang]
  {\MakeUppercase\normalfont\bfseries}
  {\thesection}{12pt}{\MakeUppercase}

%Format the subsections to be 12pt
\titleformat{\subsection}[hang]
  {\MakeUppercase\normalfont\bfseries}
  {\thesubsection}{12pt}{}

%Set the spacing between the chapter headings and the margins
\titlespacing*{\chapter}{0pt}{0pt}{24pt}
\titlespacing*{\section}{0pt}{0pt}{0pt}
\titlespacing*{\subsection}{0pt}{0pt}{0pt}
%Add dots to the table of contents for chapters
\renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}} % for chapters
%Set the spacings before and after the titles for the TOC, LOF and LOT
\setlength{\cftbeforetoctitleskip}{0.43in}
\setlength{\cftaftertoctitleskip}{21pt}
\setlength{\cftbeforelottitleskip}{0.43in}
\setlength{\cftafterlottitleskip}{21pt}
\setlength{\cftbeforeloftitleskip}{0.43in}
\setlength{\cftafterloftitleskip}{21pt}
%Set the fontsize and formatting for the TOC, LOF and LOT 
\renewcommand\contentsname{\centerline{\fontsize{16pt}{16pt}\selectfont TABLE OF CONTENTS}}
\renewcommand\listfigurename{\centerline{\fontsize{16pt}{16pt}\selectfont LIST OF FIGURES}}
\renewcommand\listtablename{\centerline{\fontsize{16pt}{16pt}\selectfont LIST OF TABLES}}
%Setting page numbers to bottom center
\pagestyle{fancy}
\cfoot{\thepage}
\rhead{}
\lhead{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
%Setting bibliography title format
\renewcommand{\bibname}{\fontsize{16pt}{24pt}\selectfont References \hfill}


\begin{document}
%Adding all the stuff that should be numbered with roman numerals
\frontmatter
\addtocontents{toc}{\textbf{Title}\hfill\textbf{Page No.}\par}
\addtocontents{toc}{\vspace{-0.3cm}}
\input{titlepage}
\input{bonafide}
\addcontentsline{toc}{chapter}{ABSTRACT}
\addtocontents{toc}{\vspace{-0.3cm}}
\input{abstract}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}
\addtocontents{toc}{\vspace{-0.3cm}}
\input{Acknowledge}
\addcontentsline{toc}{chapter}{TABLE OF CONTENTS}
\addtocontents{toc}{\vspace{-0.3cm}}
\tableofcontents
\newpage
\addcontentsline{toc}{chapter}{LIST OF TABLES}
\addtocontents{toc}{\vspace{-0.3cm}}
\listoftables
\newpage
\addcontentsline{toc}{chapter}{LIST OF FIGURES}
\addtocontents{toc}{\vspace{-0.3cm}}
\listoffigures
 
\mainmatter

\chapter{Introduction}
\fontsize{12pt}{18pt}\selectfont
\input{Chapter1}

\chapter{Review of Literature}
\fontsize{12pt}{18pt}\selectfont
\input{Chapter2}

\chapter{Data exploration}
\fontsize{12pt}{18pt}\selectfont
\input{Chapter3}

\chapter{Machine learning approach}
\fontsize{12pt}{18pt}\selectfont
\input{Chapter4}

\chapter{Code Snippets}
\fontsize{12pt}{18pt}\selectfont
Below is the implementation in Python programming language. Suitable cross validation (CV), a standard statistical resampling technique has been used. Specifically, the dataset is split into a training subset with which the learner is trained, and a testing subset which is used to assess the learner’s generalization performance. Typically some percentage of the data is left out for testing the learner, and this is known as K-fold CV, where K is usually 5 or 10. In this study, I've used 5-fold CV. The model parameters are derived using the training subset, and errors are computed using the testing subset (out-of-sample error or testing error).
For statistical confidence, the training and testing process is repeated 100 times with the dataset randomly permuted in each run prior to splitting in training and testing subsets.
\newline
\lstinputlisting{main.py}

\chapter{Results and Discussions}
\fontsize{12pt}{18pt}\selectfont
\input{Chapter6}

\chapter{Summary and Conclusions}
\fontsize{12pt}{18pt}\selectfont
\input{Chapter7}

\bibliography{tushar_refs}{}
\addcontentsline{toc}{chapter}{REFERENCES}
\bibliographystyle{unsrt}
\end{document}
